\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}

\usepackage[scale=0.75]{geometry}

\name{Philipp}{Waack}

\email{waackphilipp@gmail.com}
\homepage{waackph.github.io}
\quote{I am working as a full stack developer and data analyst. I am a team player and a curious, open-minded person.}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}



% #################################
% Lebenslauf......................

\makecvtitle


\section{Education}
% arguments 3 to 6 can be left empty
\cventry{2016--2019}{Master of Science; Computer science}{Humboldt Universität zu Berlin}{Mark: 1,9}{}{
Master thesis: \emph{Empirical study about the influence of social dimensions on the SCHUFA-Score}
}
\cventry{2012--2017}{Bachelor of Science; Media and computer science}{Technische Universität Dresden}{Mark: 2,6}{}{
Bachelorarbeit: \emph{Benutzbarkeitskonzept für VPN-basierte Anonymisierung mobiler Geräte}
}
\cventry{2002--2011}{Abitur; General matriculation standard}{Gymnasium Willhöden, Stadtteilschule Blankenese Framstraße}{Mark: 2,5}{Hamburg}{}

\section{Work experience}
\cventry{since 05/23}{Referent}{VDI/VDE-IT}{Berlin}{}{
Work at the department research and development with a focus on IT solutions and data science topics.
}
\cventry{12/19--03/23}{Data Governance Expert}{acs-plus}{Berlin}{}{
Focus on the link between Data Science, Data Engineering, Software Development and the topic of Data Governance.
}
\cventry{10/17--10/19}{Student assistant}{acs-plus}{Berlin}{Data Scientist}{
Support and autonomous accomplishment of data analysis and data modeling as well as implementation of applications to visualize and access data.
}
\cventry{04/16--09/16}{Student assistant}{Zentrum für Informationsdienste und Hochleistungsrechnen (ZIH)}{Dresden}{Editor}{
Creation of editorial content and technical instructions for the Content Management System of the ZIH at the Technischen Universität Dresden.
}

\newpage

\section{Skills}

\cvline{Scripting languages}{\hfill \break I have most experience in working with \underline{Python} and \underline{JavaScript} since I implemented professional data driven web applications using those scripting languages. I also used mainly \underline{Python} and \underline{R} in professional data analysis projects. In the voluntary work project afeefa.de I gained some experience with \underline{Ruby} and the \underline{Ruby on Rails} web framework. At work and for private projects I use \underline{Bash scripting} to automate specific tasks like creating backups.}

\cvline{Web Technologies \& Frameworks}{\hfill \break To implement web applications I have worked mainly with python \underline{Flask} and the template engine \underline{Jinja2} or implemented REST APIs to communicate with \underline{React} frontends. In some projects I also worked with \underline{Express.js} as a backend. I have experience in working with general \underline{HTML}, \underline{CSS}, \underline{JavaScript} and for dynamic user interfaces I used mainly \underline{React} and \underline{Bootstrap} as frontend frameworks.}

\cvline{Data Analysis}{\hfill \break In data analysis projects I used \underline{R} and different \underline{Python} libraries to analyse, visualize data and to train models with data. For statistical data analysis and data cleaning I worked with \underline{pandas} and \underline{SciPy}. To visualize data for analysis I used mainly \underline{matplotlib} and \underline{seaborn}. For interactive, data driven web applications I worked with \underline{D3.js} and \underline{Plotly}. To train statistical models and machine learning models I used mainly \underline{sklearn}. But I gained also some experience in working with \underline{TensorFlow} and \underline{GPflow} during my master thesis.}

\cvline{Database Technology}{\hfill \break In most web development projects and data analysis projects I worked with relational \underline{SQL Databases} - I have experience with the DBMS MariaDB, PostreSQL and SQL Server. In some projects I also worked with noSQL databases. I have experience in working with \underline{MongoDB} and gained some experience from one project in working with the graph database \underline{Neo4j}}

\cvline{Server Technology}{\hfill \break I set up multiple web applications using the \underline{Apache HTTP server} and \underline{Nginx}.}

\cvline{Versioning and Deployment}{\hfill \break For code versioning, collaboration in agile teams I work with \underline{Git} in GitLab and GitHub. To create testing and deployment pipelines I work with \underline{GitLab CI/CD} and with \underline{GitHub Actions} - depending on the project. To deploy projects I used \underline{Docker} to create containerized applications. For programming I mostly use the IDE \underline{Visual Studio Code}.}

\cvline{Programming languages}{\hfill \break In multiple game development projects I gained experience in programming with \underline{C\#} - developing games in Unity, MonoGame and plain C\#. In study projects I also gained experience in working with \underline{Java} - especially while implementing a Java based Android application to create a UI for a anonymization service during my bachelor thesis. I also gained some experience in \underline{C} during my study project to port a word embedding space model for document ranking.}

\cvline{Game Engines}{\hfill \break I developed multiple game prototypes with the framework MonoGame and the game Engine Unity.}

\cvline{Operating Systems}{\hfill \break I work frequently with \underline{Ubuntu} and \underline{Windows}. I have also experience in working with \underline{macOS}.}

\cvline{Conception \& Collaboration Tools} {\hfill \break To create frontend mockups I use \underline{Figma}. To work remotely with others and to create concepts for database models and processes I use the collaboration platform \underline{Miro}.}

\cvline{Image Processing}{\hfill \break Basic knowledge in \underline{Gimp}, \underline{Inkscape} and \underline{Scribus}. For 2D Game Projects I created Sprites and Animations in \underline{Aseprite}.}

\cvline{Office applications}{\hfill \break I frequently work open source \underline{Office} programms, \underline{PowerPoint} and \LaTeX}

\section{Languages}
\cvitemwithcomment{German}{Native language}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Spanish}{Basic knowledge}{}

\section{Internship and side jobs}
\cventry{03/14--06/14}{Praktikum}{surfcamplaspalmas.com}{Las Palmas de Gran Canaria}{Web Content Manager, SEO-Optimization}{
Emphasis on writing search engine optimized blog posts about surfing.
}
\cventry{03/12--09/12}{Various side jobs}{Edeka, Schachtrupp, Störmer Murphy and Partners}{Hamburg}{temporary job}{}
\cventry{01/12--02/12}{Internship}{Hamburger Abendblatt}{Hamburg}{Journalist}{
Internship with emphasis on autonomous local journalistic work in the district Bergedorf for the web presence of daily newspaper Hamburger Abendblatt.
}
\cventry{11/11--01/12}{Internship}{Elbe Wochenblatt}{Hamburg}{Editor}{
Research and creation of reports and stories for a local newspaper based in Hamburg.
}
\cventry{08/11--10/11}{Internship}{Infected Postproduction}{Hamburg}{Audio-visual media designer}{
Emphasis on cutting and post-production of commercials.
}

\section{Voluntary work and further training}
\cventry{09/19--10/19}{Seminar}{Journalistisches Arbeiten}{Berlin}{}{
Seminar with a focus on methods and rules for journalistic writing. Research and creation of a reportage.
}
\cventry{09/17--10/17}{Seminar}{Storytelling in Werbung, Journalismus und Politik}{Berlin}{}{
Seminar with an emphasis on different storytelling techniques and dramaturgic basics (e.g. character development and the hero's journey). Development and presentation of a story.
}
\cventry{02/17--02/19}{Voluntary}{Art project web residency: x-temporary.org}{Berlin}{Webdesign}{
Digital residency for artists. Development of a website and technical support for artists.
}
\cventry{04/15--09/16}{Voluntary}{Student newspaper ad rem}{Dresden}{Journalist}{
Research and creation of journalistic reports about technical and digital topics, higher education policies and events. Director of the technical department.
}
\cventry{08/15--04/16}{Voluntary}{Web application afeefa.de}{Dresden}{Webdesign, Ruby-on-Rails Developer}{
Development of a digital platform for offers and participation for refugees.
}

\end{document}
%% end of file `template.tex'.
